Analysis for Non-Expressive performances (ONSET)

### 2020-04-07 material/analysis/stim_n/ioi_offset.Rmd
edit .gitignore
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'IOIs Analysis for Non-Expressive performances (OFFSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of all analyses for a tempo (IOIs).

@@

```{r extract, include = FALSE}
df_ioi <- fread("./../preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

## 2. All - group
- Average normIOIs for each condition.
- Hypothesis: Participants will play slower when teaching.

>>>>

---
title: 'Analysis for Non-Expressive performances (OFFSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance from teaching-v2.0 (offsets).

@@

```{r extract, include = FALSE}
df_ioi <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

## 2. All - group
- Average normIOIs

### 2020-04-07 material/analysis/stim_n/ioi_onset.Rmd
edit .gitignore
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'IOIs Analysis for Non-Expressive performances (ONSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of all analyses for a tempo (IOIs).

@@

```{r extract, include = FALSE}
df_ioi <- fread("./../preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

>>>>

---
title: 'Analysis for Non-Expressive performances (ONSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance from teaching-v2.0 (onsets).

@@

```{r extract, include = FALSE}
df_ioi <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
